---
title: "Example Rmarkdown Report"
author: "EcoHealth Alliance"
date: "Produced on `r Sys.Date()`"
output:
  html_document:
    code_download: TRUE
    self_contained: TRUE
    toc: TRUE
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  error = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "figures/"
)


library(zscorer)
library(nipnTK)
library(nutricheckr)

targets::tar_load(
  c(nutrition_data, 
    nutrition_data_check,
    nutrition_data_issues,
    nutrition_data_clean, 
    wasting_recode, 
    wasting_prevalence)
)
```

This is an example `Rmarkdown` report produced through a workflow built on the `targets` framework, made portable using `renv`, and ran manually or automatically using `GitHub Actions`. In this example, we show a data quality check workflow report for a nutrition survey of children 6-59 months old.

## Get anthropometric data

Following is an anthropometric dataset from a single state of a West African country.

```{r, echo = FALSE}
head(nutrition_data, 20) |>
  knitr::kable(row.names = FALSE) |>
  kableExtra::kable_styling(
    bootstrap_options = c("basic"),
    full_width = FALSE,
    position = "center"
  )
```

## Perform a standard anthropometric data quality check

We perform a standard anthropometric data quality check by calculating the z-scores for the various anthropometric indices and then flag implausible values based on WHO cut-offs. We get the following results

```{r, echo = FALSE}
head(nutrition_data_check, 20) |>
  knitr::kable(row.names = FALSE) |>
  kableExtra::kable_styling(
    bootstrap_options = c("basic"),
    full_width = FALSE,
    position = "center"
  )
```

Focusing on data rows with issues, we see:

```{r, echo = FALSE}
head(nutrition_data_issues) |>
  knitr::kable(row.names = FALSE) |>
  kableExtra::kable_styling(
    bootstrap_options = c("basic"),
    full_width = FALSE,
    position = "center"
  )
```
